j_play

### 2020-12-07 scripts/Final_project.Rmd
Correlogram finalized w/ text blurb

#best one yet! Box-and-whisker plot
ggpairs(g_vic,
        upper = list(continuous = ggally_dot_and_box, combo = ggally_box_no_facet),
        lower = list (continuous = "smooth",
                      combo = "facetdensity",
                      mapping = aes(color = SPECIAL_NEEDS_CODE)))

#let's try bar graph
ggpairs(g_vic,
        upper = list(continuous = ggally_barDiag, combo = ggally_barDiag),
        lower = list (continuous = "smooth",
                      combo = "facetdensity",
                      mapping = aes(color = SPECIAL_NEEDS_CODE)))

ggally_dot_and_box(g_vic, 
                   mapping = ggplot2::aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS),
                   boxPlot = TRUE) +
  theme(axis.text.x = element_blank())

@@

>>>>

#bar graph added
ggpairs(g_vic,
        upper = list(continuous = ggally_barDiag, combo = ggally_barDiag),
        lower = list (continuous = "smooth",
                      combo = "facetdensity",
                      mapping = aes(color = SPECIAL_NEEDS_CODE)))

@@

The above correlogram isolates a single school district - Greater Victoria - as a representation of the trends observed within the whole data set. This series of plots gives a snapshot introduction for the data trends to be observed.
